MSB104_assignment1

### 2023-10-05 MSB104_assignment1.qmd
Update 05.10.23

```{r}
merged_temp <- merged_temp %>%
  mutate(id_nuts2 = substr(Sub_regions, 1,4),
          id_nuts0 = substr(Sub_regions, 1,2))
```

@@

>>>>

```{r}
merged_temp <- merged_temp %>%
  mutate(id_nuts2 = substr(Sub_regions, 1,4),
          id_nuts0 = substr(Sub_regions, 1,2)) %>%
select(Year, Sub_regions, Population, GDP, GDP_per_capita, id_nuts0, id_nuts2, gini_n2)
```

@@

Colapsing dataset by id.
Function "first(nuts2, year)

Look at the region that has 0.
It means that the gini is very low and means it is missing data.
Might be an outlier and we maybe have to deleting it.
